MSE and dynamic state variable model with sigma function

### 2018-05-16 doc/MSE_MAR_18.tex
continued on methods section

To mimic spatially heterogeneous fish populations in a mixed fishery where fishers make sequential choices on fishing areas and discarding patterns, the model was divided into a 'north' and 'south' area, and six fishing seasons per year (Table \ref{t:fishery}). There were two fish species in the model, both of which are caught by the fishery. The annual number of newborns is equal for the two species, and arbitrarily set to 400 per year. The species differ with respect to their nursery grounds: all individuals of species 1 are born in the southern area, while all individuals of species 2 are born in the northern area. The maximum age that any individual can reach was 4 years old. During their life, individuals grew in length towards the asymptotic length, which was 50 cm (Figure \ref{f:prices}). for both species. Conversion from length to weight was also equal for the two species (Table \ref{t:fishery}). Migration was parameterized so that a gradual diffusion occured between the two areas, euqal to 20 percent of the difference in abundance. For the unfished situation this led to a clear segregation of the younger ages over the two areas, while the older ages were equally distributed over the two areas  (Figure \ref{f:distributions}). Mortality from natural causes such as predation, diseases, and scenesens was assumed to be negligible, and $M_i$ set to 0.0001. Althought such absence of natural mortality impossible in reality, one could argue that the model thus mimiced long-lived species.

Age-dependent catchability links the population biomasses to the catches in the fishery, and is thus one of the crucial parameters determing the interaction between the two. In the case study, this age-dependent catchability $q_i (a)$ was assumed independent of age $a$, and equal for the two species.

@@

\subsection{Management procedure}
\label{sec2.3}
The fisheries model 
The two management strategies we considered differ by the formulae used to determine exploitation rates (HCR). These management strategies were chosen such that, if  the  management  model  was  the  correct  model  of  reality,  the corresponding  equilibrium  state  of  the  system  would  meet  the  objective  of  the  plan. For this purpose, each strategy was implemented after a period where the fishery was unmanaged, by meaned with unconstrained quota for both species.

\begin{figure}[!ht]
\centering
\label{f:distributions}
\includegraphics[width=.69\textwidth]{Figures/distributions.eps} 
\caption{Distribution of the two species over the areas as a function of age in unfished situation}
\end{figure}

@@

HCRs in the form of quotas were determined endogenously by simple and relatively linear reduction in catch if fishing mortality exceeded Fmsy. This required that fishing mortality for each stock must not exceed Fmsy, which was a limit reference point. An Optimum Yield (OY) was determined based on a MSY that must prevented overfishing, and that could be reduced from the MSY limit to take into account social, economic and precautionary considerations.  Therefore, quota was determined by a set of harvest control rule parameters consisting of the exploitaion rate at MSY.

The resulted biomass harvested rate in a year $y$, depended in the manager catch perception (based in Table~\ref{t:fishery}) and the standing biomass:
\begin{equation}
 H_{a, y, s} =\frac
                % Nominator
                {C_{i (numbers)}(a, y, s, p)}
                % Denominator
                {C_{i (numbers)}(a, y, s, p) \times B_{i (numbers)}(a, y, s, p)},
\end{equation}

@@

\begin{equation}
 H_{MSY} = YIELD CURVE..., 
\end{equation}

>>>>

To mimic spatially heterogeneous fish populations in a mixed fishery where fishers make sequential choices on fishing areas and discarding patterns, the model was divided into a 'north' and 'south' area, and six fishing seasons per year (Table \ref{t:fishery}). There were two fish species in the model, both of which are caught by the fishery. The annual number of newborns is equal for the two species, and arbitrarily set to 400 per year. The species differ with respect to their nursery grounds: all individuals of species 1 are born in the southern area, while all individuals of species 2 are born in the northern area. The maximum age that any individual can reach was 4 years old. During their life, individuals grew in length towards the asymptotic length, which was 50 cm (Figure \ref{f:prices}). for both species. Conversion from length to weight was also equal for the two species (Table \ref{t:fishery}). Migration was parameterized so that a gradual diffusion occurred between the two areas, euqal to 20 percent of the difference in abundance. For the unfished situation this led to a clear segregation of the younger ages over the two areas, while the older ages were equally distributed over the two areas  (Figure \ref{f:distributions}). Mortality from natural causes such as predation, diseases, and senescence was assumed to be negligible, and $M_i$ set to 0.0001. Although such absence of natural mortality impossible in reality, one could argue that the model thus mimicked long-lived species.

Age-dependent catchability links the population biomasses to the catches in the fishery, and is thus one of the crucial parameters determining the interaction between the two. In the case study, this age-dependent catchability $q_i (a)$ was assumed independent of age $a$, and equal for the two species.

@@

\subsection{Management procedure}
\label{sec2.3}
The input to the fisheries model consist of the the expected catch rates and the individual quota that are set for each individual in the fleet. These individual quota are set in a management procedure, which mimics the decisions of a management body. this management body makes observations on the state of the resources, and the exploitation characteristics of the fishery. In the model, the management body is assumed to collect annual observations of the biomass of the stocks, including the distribution of the biomass over the different ages. these observations stem from fisheries independent observations, such as surveys with known catchabilities. In addition, the management body makes annual observations of the catches, including their age distribution. The observed biomass and catches allow for estimation of the annual harvest rates, and the estimation of a yield per recruit curve, that is dependent on fish growth and mortality. The yield curve is dome shaped, with a maximum that is called $H_{max}$. Fishing at a harvest rate that is equal to $H_{max}$  should lead to maximum sustainable yields. The yield per recruit curve omits the potential effect of the feedback between adult biomass and recruitment, which anyway is absent in the population dynamics, that assume a constant recruitment. The Harvest Control Rule used by the management body resuslts in annual quotas such that the harvest rate in a year corresponds to $H_{max}$. These quotas are then divided equally over the individual vessels in the simulations.

\subsection{Scenarios}
\label{sec2.4}
The model is set up in three consecutive time windows. In the first window of 10 years, newborns enter the population in the absence of fishing. This results in a virgin stock status. Then, the fleet of 700 vessels starts fishing in the absence of any fisheries regulations. This window lasts xxx years and gradually results in a situation where the stocks are overfished, i.e. the harvest rates are larger than $H_{max}$. Finally, the management procedure is started where the HCR controls the annual quotas.

The two management strategies we considered differ by the formulae used to determine exploitation rates (HCR). These management strategies were chosen such that, if  the  management  model  was  the  correct  model  of  reality,  the corresponding  equilibrium  state  of  the  system  would  meet  the  objective  of  the  plan. For this purpose, each strategy was implemented after a period where the fishery was unmanaged, by meaned with unconstrained quota for both species.

\begin{figure}[!ht]
\centering
\label{f:distributions}
\includegraphics[width=.69\textwidth]{Figures/distributions.eps} 
\caption{Distribution of the two species over the areas as a function of age when stocks are in virgin stock status }
\end{figure}

@@

@@
